---
title: "Lab3"
output:
  word_document: default
  html_document: default
  pdf_document: default
date: "2022-09-19"
---
**Exercise 1: Rows & Columns**

*1.1: Uploading the Test_V_output.csv*

The dataframe was uploaded using the files tab in r studio. 

*1.2: Saving a vector with total score values*

The total score column was saved to a vector named tot_scores. I did this by assigning the vector with a c() function while referencing the total score column in the Test_V_output dataframe.
```{r}
Test_V_outputs <- read.csv(file = "//Users//nagendra//Desktop//Bioinformatics//Lecture//Test_V_output.csv"  , sep = ",", header = TRUE)
```

```{r Exercise 1.2}
tot_scores <- c(Test_V_outputs$Total.Score)
```
*1.3: Finding the Total Score of p53 molecule*

The total score value was indexed for p53 by referencing a cell in the dataframe.

```{r Exercise 1.3}
Test_V_outputs[2,"Total Score"]
```
**Exercise 2: Mean and Stddev**

*2.1: Finding the mean and stdv*

The mean of the total score column was calculated using the mean function and the tot_scores vector 
```{r Exercise 2.1}
mean(tot_scores)
```
The standard deviation of the total score column was calculated using the standard deviation function and the tot_scores vector
```{r Exercise 2.1.2}
sd(tot_scores)
```
*2.2: Finding unique PMCID*
The string split function was first used to split the strings into individuals characters. The unique function was then used to find unique PMCID values. The answer is the number of the final row of the output. 
```{r}
unique(Test_V_outputs$Paper.ID, ",")

```
**Exercise 3: Vectorization**

*3.1: Creating my own Total scores column*

```{r}
Test_V_outputs$Calc_TotScore <- (Test_V_outputs$Kind.Score+(Test_V_outputs$Evidence.Score*Test_V_outputs$Match.Score))*Test_V_outputs$Epistemic.Value
```

**Exercise 4: Subsets**

*4.1 Deleting rows and columns*

The Cell Type, Location, and organism columns were deleted using a subset function and saved to a dataframe named Test_V_outputs_short. The same dataframe was then modified further by removing all rows except the first 100 by subsetting rows. 

```{r}
Test_V_outputs_short <- subset(Test_V_outputs, select = -c(Cell.Type, Location, Organism))
Test_V_outputs_short <- Test_V_outputs_short[1:100,]
```

